---
title: "Identifying 13C incorporators"
author: "Sam Barnett"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document:
    toc: true
    toc_float: true
---

## Introduction
This notebook includes the code for running multiple window high resolution DNA-stable isotope probing (MW-HR-SIP) analysis. This analysis identifies OTUs that are enriched in heavy windows of the 13C treated gradients compared to the 12C control gradients. An enriched OTU has taken up the 13C into its DNA and is therefor an incorporator or responder. This analysis will use HTSSIP R package but should be run in R terminal rather than in this notebook since it requires use of the multiple cores and takes some time to run.

### Background
Soil microcosms contained 15g dry weight soil and consisted of a 250ml erlenmyer flask sealed with a rubber stopper. Each microcosm, except for the H2O control, were suplimented with 5 carbon substrates: soluble xylose, amino acids, and vanillin, and particulate cellulose and palmitic acid. Soluble substrates were added in Musk... solution. Treatment microcosms each had one of these substrates >99% labled with 13C. 2-3 replicate microcosms were distructively sampled on specific days depending on the substrate in question (xylose and amino acids: days 1, 3, 6, and 14, cellulose, palmitic acid, and vanillin: days 6, 14, and 30, H20 control: day 30).

### Load libraries
```{r, message=FALSE, warning=FALSE}
# Packages needed for analysis
library(dplyr)
library(tidyr)
library(phyloseq)
library(tibble)

# HTSSIP Package: For this we are using a development version of this in which case I hace modified the code of fuction DESeq2_l2fc() to put betaPrior=TRUE in the DESeq function. This was done because when DESeq2 was updated and set the default for this to FALSE. For more info check out the DESeq2 vigniette and this post: https://support.bioconductor.org/p/96975/


# Packages needed for plotting
library(ggplot2)
```

### Import and setup data
Import the full phyloseq object then subset to data from just the SIP experiment and remove negative and positive controls. Check to make sure that it fits the proper format
```{r, message=FALSE, warning=FALSE}
## Import phyloseq object
physeq = readRDS("/Users/sambarnett/Documents/Buckley Lab/FullCyc2/fullcyc2_backups_8_8_19/phyloseq/fullcyc2physeq.RDS")

## Subset to just unknown SIP samples
physeq.SIP = subset_samples(physeq, exp_type == "SIP" & sample_type == "unknown")
physeq = NULL

## Remove a few samples that were bad or incorrect. This has already been entered into the metadata
physeq.SIP.good = subset_samples(physeq.SIP, !(notes %in% c("wrong_soil", "few_sequences", "too_many_sequences")))
count_df = data.frame(count = sort(colSums(otu_table(physeq.SIP.good)))) %>%
  rownames_to_column(var="X.Sample")
physeq.SIP.good = subset_samples(physeq.SIP.good, !(X.Sample %in% count_df[count_df$count < 1000,]$X.Sample))
physeq.SIP.good = prune_taxa(taxa_sums(physeq.SIP.good) > 0, physeq.SIP.good)

## Check formatting for compatability with HTSSIP
tryCatch(
  physeq_format(physeq.SIP),
  error = function(e) e
  )

## Just for note, which samples did you remove for low count and are they important?
removed_samples = count_df %>%
  filter(count < 1000) %>%
  inner_join(data.frame(sample_data(physeq.SIP)), by="X.Sample") %>%
  select(X.Sample, library_ID, soil_ID, ecosystem, substrate, day, fraction, Buoyant_density, count) %>%
  mutate(in_window = ifelse(Buoyant_density <= 1.77 & Buoyant_density >= 1.70, "yes", "no"))
removed_samples


```

### Basic stats
```{r}
physeq.SIP

print(paste("There are", data.frame(tax_table(physeq.SIP), stringsAsFactors = FALSE) %>%
  filter(Domain == "Bacteria") %>% nrow(), 
  "Bacterial OTUs"))

print(paste("There are", data.frame(tax_table(physeq.SIP), stringsAsFactors = FALSE) %>%
  filter(Domain == "Bacteria", !(is.na(Phylum))) %>% select(Phylum) %>% unique %>% nrow(),
  "Bacterial phyla"))

```


## Ordination
Before we run the MW-HR-SIP analysis, lets check out ordinations between the treatments and controls. This will show if there is anything odd occuring in some of the fractions

```{r, message=FALSE, warning=FALSE, output=FALSE}
## Make a list of phyloseqs, one phyloseq for each 13C-12C comparison
comps = "(substrate == '12C-Con' & day == '${day}' & ecosystem == '${ecosystem}') | (substrate == '${substrate}' & day == '${day}' & ecosystem == '${ecosystem}')"
params = get_treatment_params(physeq.SIP, c('substrate', 'day', 'ecosystem'), "substrate != '12C-Con'")

physeq.SIP_l = phyloseq_subset(physeq.SIP.good, params, comps)

## Rarefy taxa in phyloseq. Also, to save on memory, remove any taxa not found in a phyloseq object
remove_0_taxa <- function(physeq){
  physeq = rarefy_even_depth(physeq)
  physeq = prune_taxa(taxa_sums(physeq) > 0, physeq)
  return(physeq)                
}
physeq.SIP_lm = lapply(physeq.SIP_l, remove_0_taxa)

## Run ordination based on Bray-Curtis
SIP.ord.df = SIP_betaDiv_ord(physeq.SIP_lm, method="bray", normalized=F)
SIP.ord.df
```

```{r}
con_light_nfrac = c()
treat_light_nfrac = c()
con_mid_nfrac = c()
treat_mid_nfrac = c()
con_heavy_nfrac = c()
treat_heavy_nfrac = c()

for (sub.physeq in physeq.SIP_l){
  con_light_nfrac = c(con_light_nfrac, nrow(filter(data.frame(sample_data(sub.physeq)), 
                                                   Buoyant_density > 1.70, Buoyant_density < 1.73, 
                                                   substrate == "12C-Con")))
  treat_light_nfrac = c(treat_light_nfrac, nrow(filter(data.frame(sample_data(sub.physeq)), 
                                                       Buoyant_density > 1.70, Buoyant_density < 1.73, 
                                                       substrate != "12C-Con")))
  con_mid_nfrac = c(con_mid_nfrac, nrow(filter(data.frame(sample_data(sub.physeq)), 
                                                   Buoyant_density > 1.72, Buoyant_density < 1.75, 
                                                   substrate == "12C-Con")))
  treat_mid_nfrac = c(treat_mid_nfrac, nrow(filter(data.frame(sample_data(sub.physeq)), 
                                                       Buoyant_density > 1.72, Buoyant_density < 1.75, 
                                                       substrate != "12C-Con")))
  con_heavy_nfrac = c(con_heavy_nfrac, nrow(filter(data.frame(sample_data(sub.physeq)), 
                                                   Buoyant_density > 1.74, Buoyant_density < 1.77, 
                                                   substrate == "12C-Con")))
  treat_heavy_nfrac = c(treat_heavy_nfrac, nrow(filter(data.frame(sample_data(sub.physeq)), 
                                                       Buoyant_density > 1.74, Buoyant_density < 1.77, 
                                                       substrate != "12C-Con")))
}

print("Min")
min(con_light_nfrac)
min(treat_light_nfrac)
min(con_mid_nfrac)
min(treat_mid_nfrac)
min(con_heavy_nfrac)
min(treat_heavy_nfrac)

print("Max")
max(con_light_nfrac)
max(treat_light_nfrac)
max(con_mid_nfrac)
max(treat_mid_nfrac)
max(con_heavy_nfrac)
max(treat_heavy_nfrac)

print("Mean")
mean(con_light_nfrac)
mean(treat_light_nfrac)
mean(con_mid_nfrac)
mean(treat_mid_nfrac)
mean(con_heavy_nfrac)
mean(treat_heavy_nfrac)

print("Median")
median(con_light_nfrac)
median(treat_light_nfrac)
median(con_mid_nfrac)
median(treat_mid_nfrac)
median(con_heavy_nfrac)
median(treat_heavy_nfrac)


```

Now plot the ordinations.
```{r, message=FALSE, warning=FALSE, fig.height=10, fig.width=20}
## First rename each comparison for better viewing
SIP.ord.clean.df = SIP.ord.df %>%
  mutate(phyloseq_subset = gsub(" \\| ", " vs.\n", 
                                gsub("\\(", "", 
                                     gsub("'\\)", "", 
                                          gsub("substrate == '", "", 
                                               gsub("' & ecosystem == '", " ", 
                                                    gsub("' & day == '", " day ", phyloseq_subset)))))))
SIP.ord.clean.df

## Also for easy reading, lets break this down by habitat
SIP.ord.agriculture.df = SIP.ord.clean.df[SIP.ord.clean.df$ecosystem == "agriculture",] %>%
  arrange(day, substrate)
SIP.ord.agriculture.df$phyloseq_subset = factor(SIP.ord.agriculture.df$phyloseq_subset, levels=unique(SIP.ord.agriculture.df$phyloseq_subset))
SIP.ord.meadow.df = SIP.ord.clean.df[SIP.ord.clean.df$ecosystem == "meadow",] %>%
  arrange(day, substrate)
SIP.ord.meadow.df$phyloseq_subset = factor(SIP.ord.meadow.df$phyloseq_subset, levels=unique(SIP.ord.meadow.df$phyloseq_subset))
SIP.ord.forest.df = SIP.ord.clean.df[SIP.ord.clean.df$ecosystem == "forest",] %>%
  arrange(day, substrate)
SIP.ord.forest.df$phyloseq_subset = factor(SIP.ord.forest.df$phyloseq_subset, levels=unique(SIP.ord.forest.df$phyloseq_subset))

?as.factor
## Plot
phyloseq_ord_plot(SIP.ord.agriculture.df, point_fill="substrate")
phyloseq_ord_plot(SIP.ord.meadow.df, point_fill="substrate")
phyloseq_ord_plot(SIP.ord.forest.df, point_fill="substrate")


```


## MW-HR-SIP
Here is the code for running MW-HR-SIP. Its best not to run this in RStudio as it requires multiple cores and takes a while.
```{r, eval=FALSE}

# Packages needed for analysis
library(dplyr)
library(tidyr)
library(phyloseq)
library(tibble)

# HTSSIP Package: For this we are using a development version of this in which case I hace modified the code of fuction DESeq2_l2fc() to put betaPrior=TRUE in the DESeq function. This was done because when DESeq2 was updated and set the default for this to FALSE. For more info check out the DESeq2 vigniette and this post: https://support.bioconductor.org/p/96975/
.libPaths("~/R/x86_64-pc-linux-gnu-library/modified_packages/HTSSIP/package/")
library(HTSSIP)
.libPaths("/home/sam/R/x86_64-pc-linux-gnu-library/3.4")
packageVersion("HTSSIP")


## Import phyloseq object
physeq = readRDS("/home/seq_data/fullCyc2/amplicon/515F-806R/final_dataset/phyloseq/fullcyc2physeq.RDS")

## Subset to just unknown SIP samples
physeq.SIP = subset_samples(physeq, exp_type == "SIP" & sample_type == "unknown")
physeq = NULL

## Remove a few samples that were bad or incorrect. This has already been entered into the metadata
physeq.SIP.good = subset_samples(physeq.SIP, !(notes %in% c("wrong_soil", "few_sequences", "too_many_sequences")))
count_df = data.frame(count = sort(colSums(otu_table(physeq.SIP.good)))) %>%
  rownames_to_column(var="X.Sample")
physeq.SIP.good = subset_samples(physeq.SIP.good, !(X.Sample %in% count_df[count_df$count < 1000,]$X.Sample))
physeq.SIP.good = prune_taxa(taxa_sums(physeq.SIP.good) > 0, physeq.SIP.good)

## Check formatting for compatability with HTSSIP
tryCatch(
  physeq_format(physeq.SIP.good),
  error = function(e) e
  )

## Make a list of phyloseqs, one phyloseq for each 13C-12C comparison
comps = "(substrate == '12C-Con' & day == '${day}' & ecosystem == '${ecosystem}') | (substrate == '${substrate}' & day == '${day}' & ecosystem == '${ecosystem}')"
params = get_treatment_params(physeq.SIP.good, c('substrate', 'day', 'ecosystem'), "substrate != '12C-Con'")

physeq.SIP_l = phyloseq_subset(physeq.SIP.good, params, comps)

remove_0_taxa <- function(physeq){
  physeq = prune_taxa(taxa_sums(physeq) > 0, physeq)
  return(physeq)                
}
physeq.SIP_lm = lapply(physeq.SIP_l, remove_0_taxa)

remove_singlegradient_taxa <- function(physeq){
  physeq.con = subset_samples(physeq, substrate == "12C-Con")
  con.count.df = data.frame(con_count = rowSums(otu_table(physeq.con))) %>%
    rownames_to_column(var="OTU") %>%
    filter(con_count > 0)
  physeq.treat = subset_samples(physeq, substrate != "12C-Con")
  treat.count.df = data.frame(treat_count = rowSums(otu_table(physeq.treat))) %>%
    rownames_to_column(var="OTU") %>%
    filter(treat_count > 0)
  good.df = inner_join(con.count.df, treat.count.df, by="OTU")
  
  physeq = prune_taxa(good.df$OTU, physeq)
  return(physeq)                
}
physeq.SIP_lmf = lapply(physeq.SIP_lm, remove_singlegradient_taxa)

## Set parameters for HTSSIP
windows = data.frame(density_min=c(1.70, 1.72, 1.74), 
                     density_max=c(1.73, 1.75, 1.77))

sparsity = seq(0.05, 0.5, 0.01)

## HTSSIP
doParallel::registerDoParallel(10)

df_l2fc = plyr::ldply(physeq.SIP_lmf, 
                      HRSIP, 
                      density_windows = windows,
                      design = ~substrate, 
                      padj_cutoff = 0.05,
                      sparsity_apply = "heavy",
                      sparsity_threshold = sparsity,
                      .parallel = TRUE)

## Save the results
saveRDS(df_l2fc, file = "/home/sam/fullCyc2_data/Final_data/df_l2fc_final.rds")

## What packages did you use?
sessionInfo()

```


Now, import the results from HTSSIP and get counts of incorperators for each treatment as well as overall incorperator counts

## Examine incorperators

First, import the l2fc file produced by HTSSIP.

```{r}
df_l2fc = readRDS("/home/sam/fullCyc2_data/Final_data/df_l2fc_final.rds")

# How many incorperators were identified in each sample and in total?
df_l2fc %>% 
  filter(padj < 0.05) %>%
  group_by(.id, sparsity_threshold) %>%
  arrange(.id) %>%
  summarize(n_incorp_OTUs = OTU %>% unique %>% length) %>%
  as.data.frame

print(length(unique(df_l2fc[df_l2fc$padj < 0.05,]$OTU)))

```

Here are the results from the other tested implimentations
```{r}
df_l2fc05 = readRDS("/home/sam/fullCyc2_data/Final_data/HTSSIP_testing/df_l2fc_p05.rds")
df_l2fcB = readRDS("/home/sam/fullCyc2_data/Final_data/HTSSIP_testing/df_l2fc_p05_bact.rds")
df_l2fcold = readRDS("/home/sam/fullCyc2_data/incorperators/df_l2fc")
df_l2fcoldcode = readRDS("/home/sam/fullCyc2_data/Final_data/HTSSIP_testing/df_l2fc_OLDdata.rds")
df_l2fcbetaPriorT = readRDS("/home/sam/fullCyc2_data/Final_data/HTSSIP_testing/df_l2fc_p05_betaPriorT.rds")
df_l2fcBG = readRDS("/home/sam/fullCyc2_data/Final_data/HTSSIP_testing/df_l2fc_p05_bothgrads.rds")

# How many incorperators were identified in each sample and in total?
df_l2fc05 %>% 
  filter(padj < 0.05) %>%
  group_by(.id, sparsity_threshold) %>%
  arrange(.id) %>%
  summarize(n_incorp_OTUs = OTU %>% unique %>% length) %>%
  as.data.frame

# How many incorperators were identified in each sample and in total?
df_l2fcB %>% 
  filter(padj < 0.05) %>%
  group_by(.id, sparsity_threshold) %>%
  arrange(.id) %>%
  summarize(n_incorp_OTUs = OTU %>% unique %>% length) %>%
  as.data.frame

# How many incorperators were identified in each sample and in total?
df_l2fcold %>% 
  filter(padj < 0.05) %>%
  group_by(.id, sparsity_threshold) %>%
  arrange(.id) %>%
  summarize(n_incorp_OTUs = OTU %>% unique %>% length) %>%
  as.data.frame

# How many incorperators were identified in each sample and in total?
df_l2fcoldcode %>% 
  filter(padj < 0.05) %>%
  group_by(.id, sparsity_threshold) %>%
  arrange(.id) %>%
  summarize(n_incorp_OTUs = OTU %>% unique %>% length) %>%
  as.data.frame

# How many incorperators were identified in each sample and in total?
df_l2fcbetaPriorT %>% 
  filter(padj < 0.05) %>%
  group_by(.id, sparsity_threshold) %>%
  arrange(.id) %>%
  summarize(n_incorp_OTUs = OTU %>% unique %>% length) %>%
  as.data.frame

# How many incorperators were identified in each sample and in total?
df_l2fcBG %>% 
  filter(padj < 0.05) %>%
  group_by(.id, sparsity_threshold) %>%
  arrange(.id) %>%
  summarize(n_incorp_OTUs = OTU %>% unique %>% length) %>%
  as.data.frame

# How many incorperators were identified in each sample and in total?
df_l2fc %>% 
  filter(padj < 0.05) %>%
  group_by(.id, sparsity_threshold) %>%
  arrange(.id) %>%
  summarize(n_incorp_OTUs = OTU %>% unique %>% length) %>%
  as.data.frame

print(length(unique(df_l2fc05[df_l2fc05$padj < 0.05,]$OTU)))
print(length(unique(df_l2fcB[df_l2fcB$padj < 0.05,]$OTU)))
print(length(unique(df_l2fcold[df_l2fcold$padj < 0.05,]$OTU)))
print(length(unique(df_l2fcoldcode[df_l2fcoldcode$padj < 0.05,]$OTU)))
print(length(unique(df_l2fcbetaPriorT[df_l2fcbetaPriorT$padj < 0.05,]$OTU)))
print(length(unique(df_l2fcBG[df_l2fcBG$padj < 0.05,]$OTU)))

print(length(unique(df_l2fc[df_l2fc$padj < 0.05,]$OTU)))

```

Add data to the incorperator dataframe. This data includes an easier to read format of the microcosm data.
```{r}

comps = "(substrate == '12C-Con' & day == '${day}' & ecosystem == '${ecosystem}') | (substrate == '${substrate}' & day == '${day}' & ecosystem == '${ecosystem}')"
params = get_treatment_params(physeq.SIP.good, c('substrate', 'day', 'ecosystem'), "substrate != '12C-Con'")

meta = params
for (i in 1:length(meta$day)){
  day =  meta$day[i]
  sub = meta$substrate[i]
  eco = meta$ecosystem[i]
  meta$.id[i] = paste("(substrate == '12C-Con' & day == '", day, "' & ecosystem == '", eco, 
                      "') | (substrate == '", sub, "' & day == '", day, "' & ecosystem == '", eco,
                      "')", sep="")
}

df_l2fc_m = inner_join(df_l2fc, meta) %>%
  mutate(treat = paste(substrate, day, ecosystem, sep="_"), day = as.numeric(as.character(day)))
df_l2fc_m

## Save this as a dataframe

write.table(df_l2fc_m, file="/home/sam/fullCyc2_data/Final_data/df_l2fc_final.txt", quote=F, sep="\t", row.names = F)

incorp_n = length(unique(df_l2fc_m[df_l2fc_m$padj < 0.05,]$OTU))
print(incorp_n)

length(unique(df_l2fcold$OTU))

```

### Taxonomy of incorperators

What phyla and class do these incorperators belong to?

```{r, fig.width=11, fig.height=7.2}
## Main dataframe
# summarizing
df_l2fc_s = df_l2fc_m %>% 
  filter(padj < 0.05) %>%
  group_by(Phylum, Class) %>%
  summarize(n_incorp_OTUs = OTU %>% unique %>% length) %>%
  ungroup()

ggplot(df_l2fc_s, aes(x=reorder(Class, -n_incorp_OTUs), y=n_incorp_OTUs)) +
    geom_bar(stat='identity', aes(fill=Phylum)) +
    labs(x='Class', y='Number of incorporator OTUs', fill="Phylum") +
    theme_bw() +
    theme(axis.text.x = element_text(angle=55, hjust=1))
      
df_l2fc_f = df_l2fc_m %>% 
  filter(padj < 0.05)
head(df_l2fc_f)

# Order samples by log2FoldChange
x = tapply(df_l2fc_f$log2FoldChange, df_l2fc_f$Class, function(x) max(x))
x = sort(x, TRUE)
df_l2fc_f$Class = factor(as.character(df_l2fc_f$Class), levels=names(x))



ggplot(df_l2fc_f, aes(x=Class, y=log2FoldChange, color=Phylum)) +
    geom_point(size=2) +
    scale_color_discrete('Phylum') +
    labs(x = 'Class', y='log2 fold change') +
    theme_bw() +
    theme(text = element_text(size=16),
          axis.text.x = element_text(angle=55, hjust=1))

```

#### Taxonomy of Bacterial incorperators

What phyla and class do these bacteria belong to?

```{r, fig.width=11, fig.height=7.2}
# summarizing
df_l2fc_s = df_l2fc_m %>%
  filter(padj < 0.05, Domain == "Bacteria") %>%
  group_by(Phylum, Class) %>%
  summarize(n_incorp_OTUs = OTU %>% unique %>% length) %>%
  ungroup()

## How many bacterial responders do you have?
bactI_n = sum(df_l2fc_s$n_incorp_OTUs)
print(paste("You have", bactI_n, "incorporator bacteria"))

ggplot(df_l2fc_s, aes(x=reorder(Class, -n_incorp_OTUs), y=n_incorp_OTUs)) +
    geom_bar(stat='identity', aes(fill=Phylum)) +
    labs(x='Class', y='Number of incorporator OTUs', fill="Phylum") +
    theme_bw() +
    theme(axis.text.x = element_text(angle=55, hjust=1))
      
df_l2fc_f = df_l2fc_m %>% 
  filter(padj < 0.05, Domain == "Bacteria")
head(df_l2fc_f)

# Order samples by log2FoldChange
x = tapply(df_l2fc_f$log2FoldChange, df_l2fc_f$Class, function(x) max(x))
x = sort(x, TRUE)
df_l2fc_f$Class = factor(as.character(df_l2fc_f$Class), levels=names(x))



ggplot(df_l2fc_f, aes(x=Class, y=log2FoldChange, color=Phylum)) +
    geom_point(size=2) +
    scale_color_discrete('Phylum') +
    labs(x = 'Class', y='log2 fold change') +
    theme_bw() +
    theme(text = element_text(size=16),
          axis.text.x = element_text(angle=55, hjust=1))
```

Out of curiosity, how many bacterial OTUs were tested and from what groups?
```{r}

bact_otu_n = length(unique(df_l2fc_m[df_l2fc_m$Domain == "Bacteria",]$OTU))

print(paste("There were", bact_otu_n, "bacterial OTUs tested"))

```


#### Taxonomy of Archaeal incorperators

What phyla and class do these archaea belong to?

```{r, fig.width=11, fig.height=7.2}
# summarizing
df_l2fc_s = df_l2fc_m %>%
  filter(padj < 0.05, Domain == "Archaea") %>%
  group_by(Phylum, Class) %>%
  summarize(n_incorp_OTUs = OTU %>% unique %>% length) %>%
  ungroup()

## How many bacterial responders do you have?
bactI_n = sum(df_l2fc_s$n_incorp_OTUs)
print(paste("You have", bactI_n, "incorporator archaea"))

ggplot(df_l2fc_s, aes(x=reorder(Class, -n_incorp_OTUs), y=n_incorp_OTUs)) +
    geom_bar(stat='identity', aes(fill=Phylum)) +
    labs(x='Class', y='Number of incorporator OTUs', fill="Phylum") +
    theme_bw() +
    theme(axis.text.x = element_text(angle=55, hjust=1))
      
df_l2fc_f = df_l2fc_m %>% 
  filter(padj < 0.05, Domain == "Archaea") %>%
  arrange(OTU)
df_l2fc_f

# Order samples by log2FoldChange
x = tapply(df_l2fc_f$log2FoldChange, df_l2fc_f$Class, function(x) max(x))
x = sort(x, TRUE)
df_l2fc_f$Class = factor(as.character(df_l2fc_f$Class), levels=names(x))



ggplot(df_l2fc_f, aes(x=Class, y=log2FoldChange, color=Phylum)) +
    geom_point(size=2) +
    scale_color_discrete('Phylum') +
    labs(x = 'Class', y='log2 fold change') +
    theme_bw() +
    theme(text = element_text(size=16),
          axis.text.x = element_text(angle=55, hjust=1))
```


Out of curiosity, how many Archaeal OTUs were tested and from what groups?
```{r}
df_l2fc_m %>%
  filter(Domain == "Archaea") %>%
  select(OTU, Phylum, Class, Order, Family, Genus, Species, ecosystem) %>%
  unique %>%
  arrange(OTU)


```


## Session Info
```{r}
sessionInfo()
```


